Nail: A practical interface generator for data formats

### 2014-04-30 paper/osdi14/eval.tex
more xxx
added tables

\subsection{Data formats}
\label{s:eval-formats}
To answer the first question, we implemented grammars for four protocols with particularly
challenging features and show that Nail is a good fit for these data formats and some aspects of
these formats would be very hard to parse with other parser generators.

In particular, we show extracts from grammars for the following protocols: 
\begin{itemize}
\item DNS messages.
\item Ethernet packets containing ARP, ICMP and UDP.
\item ZIP files.

@@

%%DNS: 
\paragraph{DNS.}

@@

However, the closest in functionality and intent is Dan Bernstein's
djbdns,\footnote{\url{http://cr.yp.to/djbdns.html}} which aims to be
a minimalist, highly secure DNS server. The latest release of djbdns,
including various support tools, is about 10,000 lines of C as measured by
\cc{sloccount}. \XXX[Show that we only count the DNS server parts, not the rest. List some
features we don't have]

@@

A similar attack was used by the fourth vulnerability, the infamous Android master key bug
\cite{saurik-masterkey}, that completely by-passed Android security multiple times through parser
differentials between the ZIP handler that checks signatures for privileged applications and the ZIP
implementations that ultimately extracts those files. Thus, valid  application bundles could be
modified to include malicious applications without breaking their signatures. Instead of both
components containing an ad-hoc archive implementation, a single Nail grammar would be reusable
across both implementations. 
\subsection{Performance.}
\input{fig-perf-dns}
To estimate the performance impact of using Nail grammars as opposed to hand-written grammars, we
benchmarked our DNS server against BIND.

>>>>

\subsection{Data formats}
\label{s:eval-formats}
To answer the first question, we implemented grammars for four protocols with particularly
challenging features and show that Nail is a good fit for these data formats and some aspects of
these formats would be very hard to parse with other parser generators. The following table lists
our example grammars, along with any features that make those protocols hard or impossible to handle
with existing grammar languages and the size of the grammar and its associated transform functions
measured in lines of code.

\begin{tabular}{l|l|l}
\textbf{Protocol} & \textbf{LOC} & \textbf{Problematic features} \\ \hline
DNS messages &  48+64 & Label compression\\
& & Count fields \\
ZIP archives & 92 + 78 & Checksums, \\ 
& & compression, offsets, \\
& &  variable length trailer\\ 
Ethernet frames & 16 & \\
ARP &  10  & \\
IP &  25 & Total Length field, options \\
UDP & 7 & Checksum, Length field \\
ICMP & 5 & Checksum \\

\end{tabular}

@@

\noindent We implemented the following applications and compare them to applications written without
Nail:

\noindent\begin{tabular}{l | l | l }
\textbf{System} & \textbf{Nail LoC}  & \textbf{LoC w/o Nail} \\
DNS server & 183 + 48 + 64 & 683 (Hammer parser)\\
&&  ~10.000 (DJBDNS)\\ 
DNS \texttt{host} tool & 98 + 48 + 64  & \XXX[TODO]\\
\texttt{unzip} & 50 + 92 + 78 & 1600 (Info-Zip) \\

\end{tabular}
%%DNS: 
\paragraph{DNS.}

@@

However, the closest in functionality and intent is Dan Bernstein's
djbdns,\footnote{\url{http://cr.yp.to/djbdns.html}} which aims to be a minimalist, highly secure,
authoritative-only DNS server. The latest release of djbdns, including various support tools, is
about 10,000 lines of C as measured by \cc{sloccount}. DJ

@@

A similar attack was used by the fourth vulnerability, the infamous Android master key bug
\cite{saurik-masterkey}, that completely by-passed Android security multiple times through parser
differentials between the ZIP handler that checks signatures for privileged applications and the ZIP
implementations that ultimately extracts those files. Thus, valid  application bundles could be
modified to include malicious applications without breaking their signatures. Instead of both
components containing an ad-hoc archive implementation, a single Nail grammar would be reusable
across both implementations.

\XXX[Add fuzzing results - no crashes]
\subsection{Performance.}
\input{fig-perf-dns}
To estimate the performance impact of using Nail grammars as opposed to hand-written grammars, we
benchmarked our DNS server against BIND.
